---
title: "Measurement trends in psychology"
subtitle: "Simulation study for priors"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  code_folding: hide
highlight: haddock
theme: flatly
toc: yes
toc_float: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

```

```{r}

library(brms)
library(tidyverse)
library(scales)
library(furrr)
library(janitor)

```

# Visualise priors

```{r}

illustrate_intercept_prior <- function(mean_prob, sd_logodds){
  
  mean_logodds <- qlogis(mean_prob)
  
  df_normal_logodds <- 
    tibble(logodds = rnorm(mean = mean_logodds, sd = sd_logodds, n = 10000000)) |>
    mutate(probability = plogis(logodds))
  
  ggplot(df_normal_logodds, aes(probability)) +
    geom_density(fill = "grey20") +
    theme_linedraw() +
    scale_x_continuous(breaks = breaks_pretty(n = 10)) +
    xlab("Probability") +
    ylab("Density") +
    ggtitle(paste0("Prevalence prior: \nnormal(M = ", round_half_up(mean_logodds, 3), "), SD = ", sd_logodds, " on the log-odds scale, \ntransformed to probabilities"))
}

#illustrate_intercept_prior(mean_prob = .70, sd_logodds = 1) # self reports of subjective experience

design <- tidyr::expand_grid(
  rep        = 1:1000,                       # Monte Carlo replications
  n          = 450,                         # sample sizes
  p_true     = c(0.02, 0.10, 0.50, 0.75),         # true probabilities (DGP)
  prior_mu_probability = c(0.02, 0.10, 0.25, 0.50),       # centre of prior on prob scale
  prior_sigma_logodds = c(1, 1.1, 1.45)      # SD on logit scale
) 

# unique priors actually used in the simulation
priors <- design |>
  distinct(prior_mu_probability, prior_sigma_logodds)

# make a plot for each prior
prior_plots <- priors |>
  mutate(plot = map2(
    .x = prior_mu_probability,
    .y = prior_sigma_logodds,
    ~ illustrate_intercept_prior(
      mean_prob  = .x,
      sd_logodds = .y
    )
  ))

# print them all to the current graphics device
prior_plots$plot |> walk(print)
```

# Simulation

Apparently doesn't run because reusing the base model doens't play nice with parallelisation, something about pointers.

```{r}

# # generate data
# generate_data <- function(n, p_true) {
#   tibble(
#     y = rbinom(n = n, size = 1, prob = p_true)
#   )
# }
# 
# # fit base model to dummy data with dummy prior
# # so that brms does not have to recompile model each iteration
# dummy_dat <- generate_data(n = 10, p_true = 0.3)
# 
# fit_logit_base <- function(dat, prior_mu_probability, prior_sigma_logodds) {
#   # 1. Compute numeric mean and sd on log-odds scale
#   mu    <- qlogis(prior_mu_probability)   # numeric
#   sigma <- prior_sigma_logodds           # already on log-odds scale
#   
#   # 2. Build prior string for Stan
#   prior_str <- sprintf("normal(%0.10f, %0.10f)", mu, sigma)
#   
#   brm(
#     formula       = bf(y ~ 1),
#     family        = bernoulli(link = "logit"),
#     data          = dat,
#     prior         = prior_string(prior_str, class = "Intercept"),
#     sample_prior  = "no",
#     iter          = 2000,
#     chains        = 1, # for parallelisation, done within furrr::future_map instead of here
#     cores         = 4,
#     refresh       = 0
#   )
# }
# 
# fitted_base <- fit_logit_base(dat = dummy_dat,
#                               prior_mu_probability = 0.1, 
#                               prior_sigma_logodds = 1.4)
# 
# 
# # analysis function
# fit_logit_update <- function(dat, prior_mu_probability, prior_sigma_logodds) {
#   # 1. Compute numeric mean and sd on log-odds scale
#   mu    <- qlogis(prior_mu_probability)   # numeric
#   sigma <- prior_sigma_logodds           # already on log-odds scale
#   
#   # 2. Build prior string for Stan
#   prior_str <- sprintf("normal(%0.10f, %0.10f)", mu, sigma)
#   
#   fit <- update(
#     object        = fitted_base,
#     formula       = bf(y ~ 1),
#     family        = bernoulli(link = "logit"),
#     data          = dat,
#     prior         = prior_string(prior_str, class = "Intercept"),
#     sample_prior  = "no",
#     iter          = 2000,
#     chains        = 4,
#     cores         = 1,     # important with furrr::multisession
#     refresh       = 0,
#     # this provides a solution for compiling the model once and reusing it, using internal caching
#     backend       = "cmdstanr"
#   )
#   
#   # 2) summarise
#   draws <- as_draws_df(fit)
#   p     <- plogis(draws$b_Intercept)
#   
#   tibble(
#     p_post_mean   = mean(p),
#     p_post_median = median(p),
#     p_post_lower  = quantile(p, 0.025),
#     p_post_upper  = quantile(p, 0.975)
#   )
# }
# 
# safe_fit_and_summarise <- purrr::possibly(fit_logit_update, otherwise = NULL)
# 
# # run simulation
# plan(multisession, workers = future::availableCores())
# 
# set.seed(42)
# 
# results <- design %>%
#   mutate(data = furrr::future_pmap(.l = list(n = n,
#                                              p_true = p_true), 
#                                    .f = generate_data,
#                                    .options = furrr_options(seed = TRUE))) |>
#   mutate(post_summary  = furrr::future_pmap(.l = list(dat = data,
#                                                       prior_mu_probability = prior_mu_probability,
#                                                       prior_sigma_logodds = prior_sigma_logodds),
#                                             .f = safe_fit_and_summarise,
#                                             .options = furrr_options(seed = TRUE))) 
# 
# # write to disk
# write_rds(results, "results.rds", compress = "gz")

```

# Simulation v2 using cmdstanr instead of update()

Vibe coding suggested changing the backend, still not working.

```{r}

# install.packages(
#   "cmdstanr",
#   repos = c(
#     "https://mc-stan.org/r-packages/",
#     "https://cloud.r-project.org"
#   )
# )
# 
# library(cmdstanr)
# cmdstanr::check_cmdstan_toolchain()
# install_cmdstan()  # one-off; may take a while



# # generate data
# generate_data <- function(n, p_true) {
#   tibble(
#     y = rbinom(n = n, size = 1, prob = p_true)
#   )
# }
# 
# 
# fit_and_summarise <- function(dat, prior_mu_probability, prior_sigma_logodds) {
#   # 1) fit
#   mu    <- qlogis(prior_mu_probability)
#   sigma <- prior_sigma_logodds
#   prior_str <- sprintf("normal(%0.10f, %0.10f)", mu, sigma)
#   
#   fit <- brm(
#     formula       = bf(y ~ 1),
#     family        = bernoulli(link = "logit"),
#     data          = dat,
#     prior         = prior_string(prior_str, class = "Intercept"),
#     sample_prior  = "no",
#     iter          = 2000,
#     chains        = 4,
#     cores         = 1,     # important with furrr::multisession
#     refresh       = 0,
#     # this provides a solution for compiling the model once and reusing it, using internal caching
#     backend       = "cmdstanr"
#   )
#   
#   # 2) summarise
#   draws <- as_draws_df(fit)
#   p     <- plogis(draws$b_Intercept)
#   
#   tibble(
#     p_post_mean   = mean(p),
#     p_post_median = median(p),
#     p_post_lower  = quantile(p, 0.025),
#     p_post_upper  = quantile(p, 0.975)
#   )
# }
# 
# safe_fit_and_summarise <- purrr::possibly(fit_and_summarise, otherwise = NULL)
# 
# # run simulation
# plan(multisession, workers = future::availableCores())
# 
# set.seed(42)
# 
# results <- design %>%
#   mutate(data = furrr::future_pmap(.l = list(n = n,
#                                              p_true = p_true), 
#                                    .f = generate_data,
#                                    .options = furrr_options(seed = TRUE))) |>
#   mutate(post_summary  = furrr::future_pmap(.l = list(dat = data,
#                                                       prior_mu_probability = prior_mu_probability,
#                                                       prior_sigma_logodds = prior_sigma_logodds),
#                                             .f = safe_fit_and_summarise,
#                                             .options = furrr_options(seed = TRUE))) 
# 
# # write to disk
# write_rds(results, "results.rds", compress = "gz")

```

# Simulation v3 using cmdstanr instead of update(), alt

Still having problems reusing the stan model while updating its priors.

```{r}

# install.packages(
#   "cmdstanr",
#   repos = c(
#     "https://mc-stan.org/r-packages/",
#     "https://cloud.r-project.org"
#   )
# )
# 
library(cmdstanr)
#cmdstanr::check_cmdstan_toolchain()
#cmdstanr::check_cmdstan_toolchain(fix = TRUE)
# install_cmdstan()  # one-off; may take a while

# generate data
generate_data <- function(n, p_true) {
  tibble(
    y = rbinom(n = n, size = 1, prob = p_true)
  )
}

# fit base model to dummy data with dummy prior
# so that brms does not have to recompile model each iteration
dummy_dat <- generate_data(n = 10, p_true = 0.3)


options(brms.backend = "cmdstanr") # ensure we use the right brms backend throughout, for parallelisation

fit_logit_base <- function(dat, prior_mu_probability, prior_sigma_logodds) {
  # 1. Compute numeric mean and sd on log-odds scale
  mu    <- qlogis(prior_mu_probability)   # numeric
  sigma <- prior_sigma_logodds           # already on log-odds scale
  
  # 2. Build prior string for Stan
  prior_str <- sprintf("normal(%0.10f, %0.10f)", mu, sigma)
  
  brm(
    formula       = bf(y ~ 1),
    family        = bernoulli(link = "logit"),
    data          = dat,
    prior         = prior_string(prior_str, class = "Intercept"),
    sample_prior  = "no",
    iter          = 2000,
    chains        = 1, # for parallelisation, done within furrr::future_map instead of here
    cores         = 4,
    refresh       = 0,
    backend       = "cmdstanr"
  )
}

fitted_base <- fit_logit_base(dat = dummy_dat,
                              prior_mu_probability = 0.1, 
                              prior_sigma_logodds = 1.4)

stan_code_path <- tempfile(pattern = "brms_sim_model", fileext = ".stan")
writeLines(stancode(fitted_base), con = stan_code_path)

# This object contains the path to the compiled C++ code.
compiled_stan_model <- cmdstanr::cmdstan_model(stan_code_path)

base_standata <- brms::make_standata(
    formula = bf(y ~ 1),
    family = bernoulli(link = "logit"),
    data = fitted_base$data,
    # Crucially, pass the prior that was used for the base compilation
    prior = fitted_base$prior
)

# analysis function
fit_logit_update <- function(dat, prior_mu_probability, prior_sigma_logodds, compiled_model, base_standata) {
  # 1. Compute numeric mean and sd on log-odds scale
  mu    <- qlogis(prior_mu_probability)   # numeric
  sigma <- prior_sigma_logodds           # already on log-odds scale
  
  # 2. Build prior string for Stan
  prior_str <- sprintf("normal(%0.10f, %0.10f)", mu, sigma)
  
  # This uses the data (dat) and the current simulation's prior.
  current_standata <- brms::make_standata(
    formula = bf(y ~ 1),
    family = bernoulli(link = "logit"),
    data = dat,
    prior = prior_string(prior_str, class = "Intercept")
  )
  
  # This updates the data (y, N) while keeping the structure defined by the base model.
  stan_data_final <- c(current_standata, base_standata)
  stan_data_final <- stan_data_final[!duplicated(names(stan_data_final))] # Remove duplicates
  
  fit <- brm(
    formula       = bf(y ~ 1),
    family        = bernoulli(link = "logit"),
    data          = dat,
    empty         = TRUE, # Stops brm from running full model creation
    stanmodel     = compiled_model, 
    stan_data     = stan_data_final,
    prior         = prior_string(prior_str, class = "Intercept"),
    sample_prior  = "no",
    iter          = 2000,
    chains        = 4,
    cores         = 1,     # important with furrr::multisession
    refresh       = 0,
    backend       = "cmdstanr"
  )
  
  # 2) summarise
  draws <- as_draws_df(fit)
  p     <- plogis(draws$b_Intercept)
  
  tibble(
    p_post_mean   = mean(p),
    p_post_median = median(p),
    p_post_lower  = quantile(p, 0.025),
    p_post_upper  = quantile(p, 0.975)
  )
}

#safe_fit_and_summarise <- purrr::possibly(fit_logit_update, otherwise = NULL)

# run simulation
plan(multisession, workers = future::availableCores())

set.seed(42)

design_and_data <- design %>%
  mutate(data = furrr::future_pmap(.l = list(n = n,
                                             p_true = p_true), 
                                   .f = generate_data,
                                   .options = furrr_options(seed = TRUE)))

results <- design_and_data |>
  mutate(post_summary  = furrr::future_pmap(.l = list(dat = data,
                                                      prior_mu_probability = prior_mu_probability,
                                                      prior_sigma_logodds = prior_sigma_logodds,
                                                      compiled_model = list(compiled_stan_model), # recycled via a list, as it is not in the data frame
                                                      base_standata = list(base_standata)), # recycled via a list, as it is not in the data frame
                                            .f = fit_logit_update,
                                            .options = furrr_options(seed = TRUE))) 

# write to disk
write_rds(results, "results.rds", compress = "gz")

```

# Summarize results

```{r}

results <- read_rds("results.rds")

# summarize results
results_summary <- results |>
  unnest(post_summary)

results_summary |>
  group_by(n, p_true, prior_mu_probability, prior_sigma_logodds) |>
  summarize(mean_ppost_mean = mean(p_post_mean),
            sd_ppost_mean = mean(p_post_mean)) |>
  ggplot(aes(p_true, mean_ppost_mean)) +
  geom_linerange(aes(ymin = mean_ppost_mean-prior_sigma_logodds, ymax = mean_ppost_mean+prior_sigma_logodds)) +
  geom_point() + 
  geom_abline(slope = 1, intercept = 0, linetype = "dotted") +
  facet_grid(prior_mu_probability ~ prior_sigma_logodds)

ggsave("results_summary.pdf", width = 6, height = 4)

```

```{r fig.height=8, fig.width=10}

results_summary |>
  group_by(p_true, prior_mu_probability, prior_sigma_logodds) |>
  arrange(p_post_mean) |>
  mutate(id = row_number()) |>
  ungroup() |>
  ggplot(aes(p_post_mean, id)) +
  geom_point() +
  ggstance::geom_linerangeh(aes(xmin = p_post_lower, xmax = p_post_upper)) +
  geom_vline(aes(xintercept = p_true), color = "red") +
  facet_grid(prior_sigma_logodds ~ prior_mu_probability)

coverage <- results_summary |>
  mutate(covered = dplyr::between(p_true, p_post_lower, p_post_upper)) |>
  group_by(p_true, prior_mu_probability, prior_sigma_logodds) |>
  summarize(coverage = mean(covered)) |>
  arrange(coverage)

write_csv(coverage, "results_coverage.csv")

```

# Session info

```{r}

sessionInfo()

```


