---
title: "Reanalysis of Baumeister et al.'s (2007) plotted data"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

Baumeister et al. (2007) "Psychology as the Science of Self-Reports and Finger Movements: Whatever Happened to Actual Behavior?" report the proportion of studies that employed measures of actual behavior from 304 studies over time. They don't provide much quantitative analysis of it. I extracted their estimates using webplotdigitizer, and here I attempt to produce an estimate of prevalence (across years) and trend (between years) taking the error associated with each estimate into account.

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```
 
```{r}

library(tidyverse)
library(brms)
library(emmeans)
library(bayestestR)
library(janitor)
library(knitr)
library(kableExtra)

dat <- read_csv("baumeister.csv", col_names = c("year", "percent")) |>
  # estimate SE
  mutate(proportion = percent/100,
         k = ceiling(304/5), # "In all, we coded 304 studies" across 5 time points
         proportion_se = sqrt((proportion * (1 - proportion)) / k),
         year_centered = year - 1986)

```

# Reproduce Baumeister's plot and add SEs and linear trend

```{r}

ggplot(data = dat, aes(x = year, y = proportion)) +
  geom_linerange(aes(ymin = proportion - proportion_se * 1.96, ymax = proportion + proportion_se * 1.96)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "black", size = 0.5) + # no error bars as this ignores the error associated with each data point
  scale_x_continuous(breaks = c(1966, 1976, 1986, 1996, 2006)) +
  scale_y_continuous(labels = scales::label_percent()) +
  coord_cartesian(ylim = c(0, 1), xlim = c(1966, 2006)) +
  theme_linedraw() +
  ylab("Studies measuring behavior") +
  xlab("Year") +
  ggtitle("") +
  theme(panel.grid.minor = element_blank())

ggsave("baumeister figure 1 recreated 2.pdf", width = 2.75, height = 2.75)

```

# Model prevalence and trend

Model the SEs to try to produce better estimates. However, brms::se() can only be used with gaussian models, so we're stuck with linear probability models.

```{r}

set.seed(42)

fit_baumeister <- brm(
  formula = proportion | se(proportion_se) ~ 1 + year_centered,
  data = dat,
  family = gaussian(),
  # weak priors
  prior = c(
    prior(normal(0, 10), class = "Intercept"),  
    prior(normal(0, 1), class = "b")  
  ),
  iter = 2000, 
  warmup = 1000,  
  chains = 4, 
  cores = 4  
)


res_prevalence_field <- fit_baumeister |>
  emmeans(specs = ~ 1,
          at = list(year_centered = 0),
          epred = TRUE) |>
  summary() |>
  select(prevalence_estimate = emmean,
         prevalence_ci_lower = lower.HPD,
         prevalence_ci_upper = upper.HPD)

res_prevalence_field |>
  mutate_if(is.numeric, janitor::round_half_up, digits = 3) |>
  kable() |>
  kable_classic(full_width = FALSE)



res_trend_field <- fit_baumeister |>
  emtrends(specs = ~ year_centered,
           var = "year_centered",
           at = list(year_centered = 0),
           epred = TRUE) |>
  summary() |>
  select(trend_estimate = year_centered.trend,
         trend_ci_lower = lower.HPD,
         trend_ci_upper = upper.HPD)

res_trend_field |>
  mutate_if(is.numeric, janitor::round_half_up, digits = 3) |>
  kable() |>
  kable_classic(full_width = FALSE)

```

# Session info

```{r}

sessionInfo()

```


