---
title: "Reanalysis of Baumeister et al.'s (2007) plotted data"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

Baumeister et al. (2007) "Psychology as the Science of Self-Reports and Finger Movements: Whatever Happened to Actual Behavior?" report the proportion of studies that employed measures of actual behavior from 304 studies over time. They don't provide much quantitative analysis of it. I extracted their estimates using webplotdigitizer, and here I attempt to produce an estimate of prevalence (across years) and trend (between years) taking the error associated with each estimate into account.

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```
 
```{r}

library(tidyverse)
library(sjPlot)
library(brms)
library(emmeans)
library(bayestestR)
library(janitor)
library(knitr)
library(kableExtra)

dat <- read_csv("baumeister.csv", col_names = c("year", "percent")) |>
  # estimate SE
  mutate(proportion = percent/100,
         k = ceiling(304/5), # "In all, we coded 304 studies" across 5 time points
         proportion_se = sqrt((proportion * (1 - proportion)) / k))
# dput(dat)

# # hardcoded to remove the need for external files
# dat <- data.frame(year = c(1966, 1976, 1986, 1996, 2006), 
#                   percent = c(45.16, 79.12, 26.16, 21.28, 15.76), 
#                   proportion = c(0.4516, 0.7912, 0.2616, 0.2128, 0.1576), 
#                   k = c(61, 61, 61, 61, 61), 
#                   proportion_se = c(0.0637, 0.0520, 0.05627, 0.0524, 0.0466))

```

# Reproduce Baumeister's plot and add SEs and linear trend

```{r}

ggplot(data = dat, aes(x = year, y = proportion)) +
  geom_linerange(aes(ymin = proportion - proportion_se * 1.96, ymax = proportion + proportion_se * 1.96)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "black", size = 0.5) + # no error bars as this ignores the error associated with each data point
  scale_x_continuous(breaks = c(1966, 1976, 1986, 1996, 2006)) +
  scale_y_continuous(labels = scales::label_percent()) +
  coord_cartesian(ylim = c(0, 1), xlim = c(1966, 2006)) +
  theme_linedraw() +
  ylab("Studies measuring behavior") +
  xlab("Year") +
  ggtitle("") +
  theme(panel.grid.minor = element_blank())

ggsave("baumeister figure 1 recreated 2.pdf", width = 2.75, height = 2.75)

```

# Model prevalence and trend

Model the SEs to try to produce better estimates. However, brms::se() can only be used with gaussian models, so we're stuck with linear probability models.

```{r}

meta_model_trend <- brm(
  formula = proportion | se(proportion_se) ~ 1 + year,
  data = dat,
  family = gaussian(),
  # weak priors
  prior = c(
    prior(normal(0, 10), class = "Intercept"),  
    prior(normal(0, 1), class = "b")  
  ),
  iter = 2000, 
  warmup = 1000,  
  chains = 4, 
  cores = 4  
)

# trend (b_year estimate)
res <- posterior_summary(meta_model_trend) |>
  as.data.frame() |>
  rownames_to_column(var = "parameter")

left_join(
  res |>
    select(parameter, estimate = Estimate, ci_lower = Q2.5, ci_upper = Q97.5) |>
    filter(parameter %in% c("b_Intercept", "b_year")) |>
    mutate_if(is.numeric, janitor::round_half_up, digits = 5),
  meta_model_trend |>
    p_direction() |>
    mutate(p = pd_to_p(pd),
           p = ifelse(p < .001, "<.001", p)) |>
    select(parameter = Parameter, p),
  by = "parameter"
) |>
  mutate_if(is.numeric, janitor::round_half_up, digits = 3) |>
  kable() |>
  kable_classic(full_width = FALSE)

# prevalence (middle year provides overall prevalence estimate)
emms_trend <- emmeans(meta_model_trend, ~ year)
emms_df_trend <- as.data.frame(emms_trend)

emms_df_trend |>
  select(prevalence = emmean, ci_lower = lower.HPD, ci_upper = upper.HPD) |>
  mutate_if(is.numeric, janitor::round_half_up, digits = 3) |>
  kable() |>
  kable_classic(full_width = FALSE)

```

# Session info

```{r}

sessionInfo()

```


