---
title: "Inter-rater reliability"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
    self_contained: true
    code_download: true
---

# TODO

- look into what they are disagreeing on, especially what-behavior, to see if they're making consistent errors. 
- Examine all examples of behavioural measures of behavior. 
- Produce a table of all the names of the measures categorised by category, as a look up table for face validity.
- use 'category' rather than remake the categories for the proportions?
- do Proportion disagreement by consensus category
- add to proportions, TODO add behavioral measure of behavior as DV



```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, include = TRUE, warning = FALSE, message = FALSE)
```

# Dependencies

```{r}

library(tidyverse)
library(janitor)
library(readxl)
library(psych)
library(irrCAC)
library(irr)
library(knitr)
library(kableExtra)

options(scipen=999)

```

# Get data

```{r}

dat_coder1 <- read_excel("../data/02 extractions for validation of the codebook/codebook_coder1.xlsx") |>
  clean_names() |>
  select(doi, study_number, measure_name, how_it_is_measured_coder1 = how_it_is_measured, what_is_measured_coder1 = what_is_measured,
         recent_tech_coder1 = used_recent_technology_only_for_what_behavior, dv_coder1 = used_as_dv_only_for_what_behavior) |>
  fill(doi, .direction = "down") |>
  fill(study_number, .direction = "down")

dat_coder2 <- read_excel("../data/02 extractions for validation of the codebook/codebook_coder2.xlsx") |>
  clean_names() |>
  select(doi, study_number, measure_name, how_it_is_measured_coder2 = how_it_is_measured, what_is_measured_coder2 = what_is_measured,
         recent_tech_coder2 = used_recent_technology_only_for_what_behavior, dv_coder2 = used_as_dv_only_for_what_behavior) |>
  fill(doi, .direction = "down") |>
  fill(study_number, .direction = "down")

```

# Combine data from the two coders

## Validation

Ensure both coders have coded the same articles and studies

```{r}

dat_coder1_summary <- dat_coder1 |>
  count(doi, name = "n_measures_coder1") 

dat_coder2_summary <- dat_coder2 |>
  count(doi, name = "n_measures_coder2") 

dat_summary <- full_join(dat_coder1_summary, 
                         dat_coder2_summary, 
                         by = c("doi")) |>
  mutate(n_measures_diff = n_measures_coder1 - n_measures_coder2) 

dat_summary |>
  count(n_measures_diff)

```

```{r}

dat_coder1_summary <- dat_coder1 |>
  count(doi, study_number, name = "n_measures_coder1") 

dat_coder2_summary <- dat_coder2 |>
  count(doi, study_number, name = "n_measures_coder2") 

dat_summary <- full_join(dat_coder1_summary, 
                         dat_coder2_summary, 
                         by = c("doi", "study_number")) |>
  mutate(n_measures_diff = n_measures_coder1 - n_measures_coder2) 

dat_summary |>
  count(n_measures_diff) 

```

## Combine and find disagreements

```{r}

dat_combined <- 
  full_join(dat_coder1,
            dat_coder2,
            by = join_by("doi", "study_number", "measure_name")) |>
  mutate(how_it_is_measured = case_when(how_it_is_measured_coder1 == how_it_is_measured_coder2 ~ how_it_is_measured_coder1,
                                        how_it_is_measured_coder1 == "Out of time" ~ "Out of time",
                                        how_it_is_measured_coder2 == "Out of time" ~ "Out of time",
                                        TRUE ~ "DISAGREEMENT"),
         what_is_measured = case_when(what_is_measured_coder1 == what_is_measured_coder2 ~ what_is_measured_coder1,
                                      what_is_measured_coder1 == "Out of time" ~ "Out of time",
                                      what_is_measured_coder2 == "Out of time" ~ "Out of time",
                                      TRUE ~ "DISAGREEMENT"),
         dv = case_when(dv_coder1 == dv_coder2 ~ dv_coder1,
                        is.na(dv_coder1) & is.na(dv_coder2) ~ NA_character_,
                        dv_coder1 == "Out of time" ~ "Out of time",
                        dv_coder2 == "Out of time" ~ "Out of time",
                        TRUE ~ "DISAGREEMENT"),
         recent_tech = case_when(recent_tech_coder1 == recent_tech_coder2 ~ recent_tech_coder1,
                                 is.na(recent_tech_coder1) & is.na(recent_tech_coder2) ~ NA_character_,
                                 recent_tech_coder1 == "Out of time" ~ "Out of time",
                                 recent_tech_coder2 == "Out of time" ~ "Out of time",
                                 TRUE ~ "DISAGREEMENT"))

matching_row_n <- nrow(dat_coder1) == nrow(dat_coder2) & nrow(dat_coder1) == nrow(dat_combined)

write_csv(dat_combined, "../data/02 extractions for validation of the codebook/codebook_combined_before_resolution.csv")

```

Same number of rows in each of the codebooks and the combined one: `r matching_row_n`

## Resolve disagreements

Manual step done outside of R - create 'codebook_combined_resolved_disagreements.csv' from 'codebook_combined_before_resolution.csv', creating the following columns by consensus:

- `how_it_is_measured_consensus`
- `what_is_measured_consensus` 
- `recent_tech_consensus`
- `dv_consensus`

```{r}

dat_resolved <- read_excel("../data/02 extractions for validation of the codebook/codebook_combined_resolved_disagreements.xlsx") |>
  mutate(category = case_when(is.na(how_it_is_measured_consensus) ~ NA_character_,
                              how_it_is_measured_consensus == "Indeterminable" ~ NA_character_,
                              how_it_is_measured_consensus == "Out of time" ~ NA_character_,
                              is.na(what_is_measured_consensus) ~ NA_character_,
                              what_is_measured_consensus == "Indeterminable" ~ NA_character_,
                              what_is_measured_consensus == "Out of time" ~ NA_character_,
                              TRUE ~ paste(how_it_is_measured_consensus, what_is_measured_consensus)))


dat_coder_gpt <- read_excel("../data/02 extractions for validation of the codebook/codebook_combined_with_chatgpt.xlsx") |>
  mutate(category = case_when(is.na(how_it_is_measured_consensus) ~ NA_character_,
                              how_it_is_measured_consensus == "Indeterminable" ~ NA_character_,
                              how_it_is_measured_consensus == "Out of time" ~ NA_character_,
                              is.na(what_is_measured_consensus) ~ NA_character_,
                              what_is_measured_consensus == "Indeterminable" ~ NA_character_,
                              what_is_measured_consensus == "Out of time" ~ NA_character_,
                              TRUE ~ paste(how_it_is_measured_consensus, what_is_measured_consensus))) |>
  select(-starts_with("chagpt"))

identical(dat_resolved, dat_coder_gpt)

common_cols <- intersect(names(dat_resolved), names(dat_coder_gpt))


# If you want a more detailed report of any differences:
diff_summary <- lapply(common_cols, function(col) {
  same <- identical(dat_resolved[[col]], dat_coder_gpt[[col]])
  list(column = col, identical = same)
})
diff_summary <- bind_rows(lapply(diff_summary, as.data.frame))

# Show only columns that differ (if any)
diff_summary %>% filter(!identical)


```

# Proportion disagreement

```{r}

dat_resolved |>
  select(doi, how_it_is_measured, what_is_measured, dv, recent_tech) |>
  pivot_longer(cols = -doi,
               names_to = "dimension", 
               values_to = "coding") |>
  group_by(dimension) |>
  summarize(percent_disagreement = mean(coding == "DISAGREEMENT"))

dat_resolved |>
  select(doi, how_it_is_measured, what_is_measured, dv, recent_tech) |>
  pivot_longer(cols = -doi,
               names_to = "dimension", 
               values_to = "coding") |>
  group_by(dimension) |>
  summarize(percent_out_of_time = mean(coding == "Out of time"))

dat_resolved |>
  select(doi, how_it_is_measured, what_is_measured, dv, recent_tech) |>
  pivot_longer(cols = -doi,
               names_to = "dimension", 
               values_to = "coding") |>
  group_by(dimension) |>
  summarize(percent_disagreement_or_out_of_time = mean(coding %in% c("DISAGREEMENT", "Out of time")))

```

# Inter-Rater Reliability

There are no widely used interpretation cutoffs for Iota and AC1/AC2 specifically. Although the Landis & Koch (1977)/Altman bands for Kappa are both used for other IRR metrics and yet criticized. For better or worse, we'll use them.

- ≥0.40 → Moderate agreement
- ≥0.60 → Good agreement
- ≥0.80 → Very good agreement

## Wrangle

```{r}

# how
dat_doi_level_codings_how_r1 <- dat_resolved |>
  select(doi, measure_name, how_it_is_measured_coder1) |>
  count(doi, how_it_is_measured_coder1) |>
  mutate(present = n > 0) |>
  select(-n) |>
  pivot_wider(names_from = "how_it_is_measured_coder1",
              values_from = "present",
              names_prefix = "r1_") |>
  janitor::clean_names() |>
  mutate(
    r1_indeterminable = if_else(is.na(r1_indeterminable), FALSE, r1_indeterminable),
    #r1_out_of_time = if_else(is.na(r1_out_of_time), FALSE, r1_out_of_time),
    r1_self_report = if_else(is.na(r1_self_report), FALSE, r1_self_report),
    r1_behavioral_frequency_duration_latency = if_else(is.na(r1_behavioral_frequency_duration_latency), FALSE, r1_behavioral_frequency_duration_latency),
    r1_neuro_bio_physiological = if_else(is.na(r1_neuro_bio_physiological), FALSE, r1_neuro_bio_physiological),
    r1_test = if_else(is.na(r1_test), FALSE, r1_test)
    #r1_na = if_else(is.na(r1_na), FALSE, r1_na),
  )

dat_doi_level_codings_how_r2 <- dat_resolved |>
  select(doi, measure_name, how_it_is_measured_coder2) |>
  count(doi, how_it_is_measured_coder2) |>
  mutate(present = n > 0) |>
  select(-n) |>
  pivot_wider(names_from = "how_it_is_measured_coder2",
              values_from = "present",
              names_prefix = "r2_") |>
  janitor::clean_names() |>
  mutate(
    r2_indeterminable = if_else(is.na(r2_indeterminable), FALSE, r2_indeterminable),
    #r2_out_of_time = if_else(is.na(r2_out_of_time), FALSE, r2_out_of_time),
    r2_self_report = if_else(is.na(r2_self_report), FALSE, r2_self_report),
    r2_behavioral_frequency_duration_latency = if_else(is.na(r2_behavioral_frequency_duration_latency), FALSE, r2_behavioral_frequency_duration_latency),
    r2_neuro_bio_physiological = if_else(is.na(r2_neuro_bio_physiological), FALSE, r2_neuro_bio_physiological),
    r2_test = if_else(is.na(r2_test), FALSE, r2_test)
    #r2_na = if_else(is.na(r2_na), FALSE, r2_na),
  )

dat_doi_level_codings_how_consensus <- dat_resolved |>
  select(doi, measure_name, how_it_is_measured_consensus) |>
  count(doi, how_it_is_measured_consensus) |>
  mutate(present = n > 0) |>
  select(-n) |>
  pivot_wider(names_from = "how_it_is_measured_consensus",
              values_from = "present",
              names_prefix = "consensus_") |>
  janitor::clean_names() |>
  mutate(
    consensus_indeterminable = if_else(is.na(consensus_indeterminable), FALSE, consensus_indeterminable),
    #consensus_out_of_time = if_else(is.na(consensus_out_of_time), FALSE, consensus_out_of_time),
    consensus_self_report = if_else(is.na(consensus_self_report), FALSE, consensus_self_report),
    consensus_behavioral_frequency_duration_latency = if_else(is.na(consensus_behavioral_frequency_duration_latency), FALSE, consensus_behavioral_frequency_duration_latency),
    consensus_neuro_bio_physiological = if_else(is.na(consensus_neuro_bio_physiological), FALSE, consensus_neuro_bio_physiological),
    consensus_test = if_else(is.na(consensus_test), FALSE, consensus_test)
    #consensus_na = if_else(is.na(consensus_na), FALSE, consensus_na),
  )

dat_doi_level_codings_how <- dat_doi_level_codings_how_r1 |>
  full_join(dat_doi_level_codings_how_r2, by = "doi") |>
  full_join(dat_doi_level_codings_how_consensus, by = "doi")

# what
dat_doi_level_codings_what_r1 <- dat_resolved |>
  select(doi, measure_name, what_is_measured_coder1) |>
  count(doi, what_is_measured_coder1) |>
  mutate(present = n > 0) |>
  select(-n) |>
  pivot_wider(names_from = "what_is_measured_coder1",
              values_from = "present",
              names_prefix = "r1_") |>
  janitor::clean_names() |>
  mutate(
    r1_indeterminable                      = if_else(is.na(r1_indeterminable),                      FALSE, r1_indeterminable),
    r1_out_of_time                         = if_else(is.na(r1_out_of_time),                         FALSE, r1_out_of_time),
    r1_subjective_experience               = if_else(is.na(r1_subjective_experience),               FALSE, r1_subjective_experience),
    r1_behavior                            = if_else(is.na(r1_behavior),                            FALSE, r1_behavior),
    r1_neuro_bio_physiology                = if_else(is.na(r1_neuro_bio_physiology),                FALSE, r1_neuro_bio_physiology),
    r1_mental_ability_or_cognitive_process = if_else(is.na(r1_mental_ability_or_cognitive_process), FALSE, r1_mental_ability_or_cognitive_process)
    #r1_na                                  = if_else(is.na(r1_na),                                  FALSE, r1_na),
  )

dat_doi_level_codings_what_r2 <- dat_resolved |>
  select(doi, measure_name, what_is_measured_coder2) |>
  count(doi, what_is_measured_coder2) |>
  mutate(present = n > 0) |>
  select(-n) |>
  pivot_wider(names_from = "what_is_measured_coder2",
              values_from = "present",
              names_prefix = "r2_") |>
  janitor::clean_names() |>
  mutate(
    r2_indeterminable                      = if_else(is.na(r2_indeterminable),                      FALSE, r2_indeterminable),
    r2_out_of_time                         = if_else(is.na(r2_out_of_time),                         FALSE, r2_out_of_time),
    r2_subjective_experience               = if_else(is.na(r2_subjective_experience),               FALSE, r2_subjective_experience),
    r2_behavior                            = if_else(is.na(r2_behavior),                            FALSE, r2_behavior),
    r2_neuro_bio_physiology                = if_else(is.na(r2_neuro_bio_physiology),                FALSE, r2_neuro_bio_physiology),
    r2_mental_ability_or_cognitive_process = if_else(is.na(r2_mental_ability_or_cognitive_process), FALSE, r2_mental_ability_or_cognitive_process)
    #r2_na                                  = if_else(is.na(r2_na),                                  FALSE, r2_na),
  )

dat_doi_level_codings_what_consensus <- dat_resolved |>
  select(doi, measure_name, what_is_measured_consensus) |>
  count(doi, what_is_measured_consensus) |>
  mutate(present = n > 0) |>
  select(-n) |>
  pivot_wider(names_from = "what_is_measured_consensus",
              values_from = "present",
              names_prefix = "consensus_") |>
  janitor::clean_names() |>
  mutate(
    consensus_indeterminable = if_else(is.na(consensus_indeterminable), FALSE, consensus_indeterminable),
    #consensus_out_of_time = if_else(is.na(consensus_out_of_time), FALSE, consensus_out_of_time),
    consensus_subjective_experience = if_else(is.na(consensus_subjective_experience), FALSE, consensus_subjective_experience),
    consensus_behavior = if_else(is.na(consensus_behavior), FALSE, consensus_behavior),
    consensus_neuro_bio_physiology = if_else(is.na(consensus_neuro_bio_physiology), FALSE, consensus_neuro_bio_physiology),
    consensus_mental_ability_or_cognitive_process = if_else(is.na(consensus_mental_ability_or_cognitive_process), FALSE, consensus_mental_ability_or_cognitive_process)
    #consensus_na = if_else(is.na(consensus_na), FALSE, consensus_na),
  )

dat_doi_level_codings_what <- dat_doi_level_codings_what_r1 |>
  full_join(dat_doi_level_codings_what_r2, by = "doi") |>
  full_join(dat_doi_level_codings_what_consensus, by = "doi")

```

## Across all 8 categories 

(4 categories * 2 dimensions) applied at the DOI level: Iota metric

```{r}

r1_items <- full_join(
  dat_doi_level_codings_how_r1,
  dat_doi_level_codings_what_r1,
  by = "doi"
) |>
  arrange(doi) %>%
  rename_with(~ gsub("r1_", "", .x)) |>
  select(self_report, test, behavioral_frequency_duration_latency, neuro_bio_physiological, 
         subjective_experience, mental_ability_or_cognitive_process, behavior, neuro_bio_physiology) 

r2_items <- full_join(
  dat_doi_level_codings_how_r2,
  dat_doi_level_codings_what_r2,
  by = "doi"
) |>
  arrange(doi) %>%
  rename_with(~ gsub("r2_", "", .x)) |>
  select(self_report, test, behavioral_frequency_duration_latency, neuro_bio_physiological, 
         subjective_experience, mental_ability_or_cognitive_process, behavior, neuro_bio_physiology) 

items <- intersect(colnames(r1_items), colnames(r2_items))

rating_list <- lapply(items, function(item) {
  cbind(
    r1 = r1_items[[item]],
    r2 = r2_items[[item]]
  )
})
names(rating_list) <- items

res_iota <- iota(rating_list, scaledata = "nominal")



# bootstrap CI over subjects (DOIs)
set.seed(123)

n_subj <- nrow(rating_list[[1]])   # number of DOIs
B      <- 5000L                    # number of bootstrap resamples

iota_boot <- numeric(B)

for (b in seq_len(B)) {
  idx <- sample.int(n_subj, n_subj, replace = TRUE)  # resample DOIs
  rating_list_b <- lapply(rating_list, function(mat) {
    mat[idx, , drop = FALSE]
  })
  iota_boot[b] <- iota(rating_list_b, scaledata = "nominal")$value
}

# percentile 95% CI
cis <- quantile(iota_boot, probs = c(0.025, 0.975))

data.frame(iota = as.numeric(res_iota$value),
           ci_lower = as.numeric(cis[1]),
           ci_upper = as.numeric(cis[2])) |>
  round_half_up(2)

```

## For individual categories DOI level 

Applied at the DOI level: Gwent's AC1 metric.

| Statistic                      | Chance-corrected?  | Prevalence-sensitive?  | Suitable for binary data?  | Notes                                                                  |
|:-------------------------------|:-------------------|:-----------------------|:---------------------------|:-----------------------------------------------------------------------|
| **Cohen’s κ**                  | Yes                | High                   | Yes                        | Common but suffers from prevalence & bias paradoxes.                   |
| **Percent agreement (Po)**     | No                 | High                   | Yes                        | Purely descriptive; inflated under skew, which is present in our data. |
| **Krippendorff’s α**           | Yes                | Medium                 | Yes                        | Handles missing data; more general than κ/AC1.                         |
| **Gwet’s AC1**                 | Yes                | Low                    | Yes                        | Best κ alternative; avoids κ paradox.                                  |

```{r}

tidy_ac1 <- function(.data, var1, var2){
  res <- .data |>
    select({{var1}}, {{var2}}) %>%
    gwet.ac1.raw(.)
  
  prop_agreement <- .data |>
    summarize(prop_agreement = mean({{var1}} == {{var2}})) |>
    pull(prop_agreement)
  
  res$est |>
    select(gwents_ac1 = coeff.val,
           conf.int) |>
    mutate(conf.int = str_remove(conf.int, "\\("),
           conf.int = str_remove(conf.int, "\\)")) |>
    separate(conf.int, into = c("ci_lower", "ci_upper"), sep = ",") |>
    mutate(ci_lower = as.numeric(ci_lower),
           ci_upper = as.numeric(ci_upper)) |>
    mutate(proportion_agreement = prop_agreement) |>
    select(proportion_agreement, gwents_ac1, ci_lower, ci_upper)
}

results_ac1 <- bind_rows(
  tidy_ac1(dat_doi_level_codings_how, r1_self_report, r2_self_report)                                                     |> mutate(dimension = "how", category = "subjective experience"),
  tidy_ac1(dat_doi_level_codings_how, r1_behavioral_frequency_duration_latency, r2_behavioral_frequency_duration_latency) |> mutate(dimension = "how", category = "ability"),
  tidy_ac1(dat_doi_level_codings_how, r1_neuro_bio_physiological, r2_neuro_bio_physiological)                             |> mutate(dimension = "how", category = "behavior"),
  tidy_ac1(dat_doi_level_codings_how, r1_test, r2_test)                                                                   |> mutate(dimension = "how", category = "neuro"),
  
  tidy_ac1(dat_doi_level_codings_what, r1_subjective_experience, r2_subjective_experience)                                |> mutate(dimension = "what", category = "subjective experience"),
  tidy_ac1(dat_doi_level_codings_what, r1_mental_ability_or_cognitive_process, r2_mental_ability_or_cognitive_process)    |> mutate(dimension = "what", category = "ability"),
  tidy_ac1(dat_doi_level_codings_what, r1_behavior, r2_behavior)                                                          |> mutate(dimension = "what", category = "behavior"),
  tidy_ac1(dat_doi_level_codings_what, r1_neuro_bio_physiology, r2_neuro_bio_physiology)                                  |> mutate(dimension = "what", category = "neuro")
) |>
  relocate(category) |>
  relocate(dimension) 

results_ac1 |>
  mutate_if(is.numeric, round_half_up, digits = 2) |>
  kable() |>
  kable_classic(full_width = FALSE)

```

## For individual categories measure level

Applied at the measure level: AC2_nominal 

Could also be used for the measure-level codings, but these aren't directly relied on by the analysis.

TODO

# Proportions

```{r}

dat_doi_level_codings_what |>
  count(consensus_subjective_experience) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

dat_doi_level_codings_what |>
  count(consensus_behavior) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

dat_doi_level_codings_what |>
  count(consensus_mental_ability_or_cognitive_process) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

dat_doi_level_codings_what |>
  count(consensus_neuro_bio_physiology) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

```

```{r}

dat_doi_level_codings_how |>
  count(consensus_self_report) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

dat_doi_level_codings_how |>
  count(consensus_behavioral_frequency_duration_latency) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

dat_doi_level_codings_how |>
  count(consensus_test) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

dat_doi_level_codings_how |>
  count(consensus_neuro_bio_physiological) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

```

```{r}

dat_doi_level_codings <- 
  full_join(dat_doi_level_codings_how, 
            dat_doi_level_codings_what,
            by = "doi") |>
  select(doi, starts_with("consensus")) |>
  mutate(behavioral_measure_of_behavior = consensus_behavior & consensus_behavioral_frequency_duration_latency,
         self_report_of_subjective_experience = consensus_self_report & consensus_subjective_experience,
         test_of_ability = consensus_mental_ability_or_cognitive_process & consensus_test, 
         neuro_neuro = consensus_neuro_bio_physiological & consensus_neuro_bio_physiology)


dat_doi_level_codings |>
  count(self_report_of_subjective_experience) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

dat_doi_level_codings |>
  count(behavioral_measure_of_behavior) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

dat_doi_level_codings |>
  count(test_of_ability) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

dat_doi_level_codings |>
  count(neuro_neuro) |>
  mutate(prop = janitor::round_half_up(n/sum(n), 3)) |>
  arrange(desc(n))

```


# Session info

```{r}

sessionInfo()

```

