---
title: "Reanalysis of association between self-reported vs behavioral measures of sleep quality and duration"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies and data

Sources:

- Cudney et al.'s (2022) review doi https://doi.org/10.5664/jcsm.9708 - correlations between single time point self-report measures and behavioral measures of sleep (Table 1)
- Jackson et al. (2020) doi https://doi.org/10.1093/sleep/zsz246 - correlations between single time point self-report measures and behavioral measures of sleep (abstract)

Note that data was taken at face value. No checking for extraction accuracy or completeness, no tests of publication bias, etc. 
 
```{r}

library(tidyverse)
library(brms)
library(emmeans)
library(janitor)
library(knitr)
library(kableExtra)

dat <- read_csv("../../data/jackson et al. 2020 and cudney et al. 2022/jackson_cudney.csv") |>
  mutate(r_corrected_se = sqrt((1 - r_corrected^2) / (n - 2)))

```

# Weighted averages

```{r}

dat_cudney <- dat |>
  filter(secondary_source == "Cudney et al, 2022")

n_cudney <- dat_cudney |>
  distinct(source, .keep_all = TRUE) |>
  summarize(total_n = sum(n)) |>
  pull(total_n)

k_cudney <- dat_cudney |>
  distinct(source) |>
  count(name = "k") |>
  pull(k)

weighted_r_cudney <- weighted.mean(x = dat_cudney$r_corrected, w = dat_cudney$n) |>
  janitor::round_half_up(digits = 2)


dat_jackson <- dat |>
  filter(secondary_source == "Jackson et al, 2020")

n_jackson <- dat_jackson |>
  distinct(source, .keep_all = TRUE) |>
  summarize(total_n = sum(n)) |>
  pull(total_n)

weighted_r_jackson <- weighted.mean(x = dat_jackson$r_corrected, w = dat_jackson$n) |>
  janitor::round_half_up(digits = 2)

```

Cudney et al. (2022): Weighted *r* = `r weighted_r_cudney`, n = `r n_cudney`, k = `r k_cudney`.

Jackson et al (2020): *r* = `r weighted_r_jackson`, n = `r n_jackson`

# Session info

```{r}

sessionInfo()

```


