---
title: "Stratified random sampling of records by journal and year"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
    self_contained: true
    code_download: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, include = TRUE, warning = FALSE, message = FALSE)
```

# Dependencies

```{r}

library(tidyverse)
library(janitor)
library(knitr)
library(kableExtra)

options(scipen=999)

```

# Load and clean data

```{r}
target_n_per_journal_per_year <- 25
```

NB n_available for PLOS ONE is estimated from a 2.5% prevalence!

```{r fig.height=25, fig.width=10}

data_processed <- read_rds("../data/04 processed/data_processed.rds") |>
  distinct(DOI, .keep_all = TRUE) |>
  #filter(more_than_30_citations_per_year) |>
  # exclude titles including the string "review" unless it also contains the string "meta" in order to exclude systematic reviews without meta-analyses
  filter(!str_detect(title, regex("review", ignore_case = TRUE)) | 
           str_detect(title, regex("meta", ignore_case = TRUE))) |>
  # tidy up titles
  mutate(title = str_replace(title, "<scp>\\s*COVID\\s*</scp>", "COVID"),
         title = str_replace_all(title, "\\s+", " "),
         title = str_remove_all(title, "<[^>]+>"),
         journal = str_remove_all(journal, "\n"),
         journal = case_when(journal == "PLOS ONE" ~ "PLoS ONE",
                             journal == "PLoS One" ~ "PLoS ONE",
                             journal == "Memory &amp; Cognition" ~ "Memory and Cognition",
                             journal == "Journal of Clinical Child &amp; Adolescent Psychology" ~ "Journal of Clinical Child and Adolescent Psychology",
                             journal == "Journal of Experimental Psychology: Human Perception and                    Performance" ~ "Journal of Experimental Psychology: Human Perception and Performance",
                             journal == "Journal of Experimental Psychology: Learning, Memory, and                    Cognition" ~ "Journal of Experimental Psychology: Learning, Memory, and Cognition",
                             TRUE ~ journal))

res_sampling <- data_processed |>
  group_by(journal) |>
  summarize(
    n_available = n(),
    min_year = min(year, na.rm = TRUE),
    max_year = max(year, na.rm = TRUE),
    year_span = max_year - min_year + 1
  ) |>
  mutate(
    # about 2.5% of PLOS ONE articles are psych studies on humans, from training data
    n_available = case_when(journal != "PLoS ONE" ~ n_available,
                            journal == "PLoS ONE" ~ ceiling(n_available*0.025)), 
    articles_per_year = round_half_up(n_available / year_span, 1),
    # Percentage of total available records that would be taken 
    # if you sampled 100 per year across the span
    sampling_fraction_pct = round_half_up((target_n_per_journal_per_year * year_span) / n_available * 100, 0),
    # Cap the fraction at 100% if the journal has fewer than 100 articles/year
    sampling_fraction_pct = pmin(sampling_fraction_pct, 100)
  ) |>
  arrange(desc(n_available))

res_sampling |>
  kable() |>
  kable_classic(full_width = FALSE)

write_csv(res_sampling, "../data/04 processed/data_sampling_counts.csv")

data_processed |>
  count(journal, year) |>
  group_by(journal) |>
  ggplot(aes(year, n)) +
  geom_vline(xintercept = 2024.5, linetype = "dashed", color = "darkred") +
  geom_point() +
  geom_line() +
  ylab("N articles published") +
  facet_wrap(~ journal, scales = "free_y", ncol = 3)

```

Total articles in testing if 30 journals * 19 years * `r target_n_per_journal_per_year` articles per year = `r 30 * 19 * target_n_per_journal_per_year`.

# Sample

## Training

### PLoS ONE

Select a random sample of 50 articles specifically from PLoS ONE to serve as an initial subset for training or manual coding.

```{r}

set.seed(42)

data_processed_subset_training_plosone <- data_processed |>
  filter(journal == "PLoS ONE") |>
  slice_sample(n = 50)

write_csv(data_processed_subset_training_plosone,
          "../data/04 processed/data_processed_subset_training_plosone.csv")

```

### Sampling

Load the manually coded PLoS ONE data, filter for relevant psychological studies involving human participants, and then combine these with a stratified sample of 10 articles from all other journals to create a diverse training set.

```{r}

# human coding of psych studies on human participants
data_processed_subset_training_plosone_all <- 
  read_csv("../data/04 processed/data_processed_subset_training_plosone_coded.csv")

data_processed_subset_training_plosone_all |>
  count(psych_study_on_human_participants) |>
  mutate(percent = round(n/sum(n)*100, 1))

data_processed_subset_training_plosone <- data_processed_subset_training_plosone_all |>
  filter(psych_study_on_human_participants)

set.seed(42)

data_processed_subset_training <- data_processed |>
  filter(journal != "PLoS ONE") |>
  group_by(journal) |>
  slice_sample(n = 10) |>
  bind_rows(data_processed_subset_training_plosone)

write_csv(data_processed_subset_training,
          "../data/04 processed/data_processed_subset_training.csv")

nrow(data_processed_subset_training)

data_processed_subset_training |>
  count(journal)

```

## Testing


TODO DO WE NEED TO OVERSAMPLE ARTICLES HERE, BECAUSE THEY STILL HAVE TO BE SCREENED AGAINST THE INCLUSION/EXCLUSION CRITERIA?



Identify all available data that was not used in the training set and extract a longitudinal sample of 150 PLoS ONE articles per year for testing purposes.

NB from the training data, only about 2.5% of PLOS ONE articles are psych studies (so round down to 2%). Adding this as a multiplier: n_per_journal_per_year / prevalence * years = `r n_per_journal_per_year / 0.02 * 19`. 9500/19*0.02

```{r}

data_processed_subset_training <- read_csv("../data/04 processed/data_processed_subset_training.csv")

data_processed_without_training <- data_processed |>
  anti_join(data_processed_subset_training, by = join_by("DOI"))

set.seed(42)

data_processed_subset_testing_plosone <- data_processed_without_training |>
  filter(journal == "PLoS ONE") |>
  group_by(year) |>
  slice_sample(n = target_n_per_journal_per_year / 0.02) 

write_csv(data_processed_subset_testing_plosone,
          "../data/04 processed/data_processed_subset_testing_plosone.csv")

nrow(data_processed_subset_testing_plosone)

```

`data_processed_subset_testing_plosone.csv` needs to be converted to `data_processed_subset_testing_plosone_coded.csv` through an LLM screening process, adding the psych_study_on_human_participants (TRUE/FALSE) column. Place it in the same directory to be read back in the next chunk.

Filter the coded testing subset for valid human participant studies and assemble the final testing dataset by sampling 10 articles per journal per year from the remaining non-PLoS ONE data.

```{r}

data_processed_subset_testing_plosone <- 
  read_csv("../data/04 processed/data_processed_subset_testing_plosone_coded.csv") |>
  filter(psych_study_on_human_participants)

set.seed(42)

data_processed_subset_testing <- data_processed_without_training |>
  filter(journal != "PLoS ONE") |>
  group_by(journal, year) |>
  slice_sample(n = target_n_per_journal_per_year) |>
  bind_rows(data_processed_subset_testing_plosone) # TODO uncomment this line once the plos one files are screened.

write_csv(data_processed_subset_testing,
          "../data/04 processed/data_processed_subset_testing.csv")

nrow(data_processed_subset_testing)

```

# Session info

```{r}

sessionInfo()

```

